### 2023-11-28 main.tex
kk

{\color{red} I do not understand why we immediately start with XXX although the duality approach is much more general.}
For the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}. The results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable quantum spin chain, i.e. the XXX Heisenberg Hamiltonian with ${su}(2)$ spins of value $s=1/2$.
In this paper, we investigate the multispecies analog of the exclusion process in the boundary-driven context \cite{vanicat2017exact}, i.e. the {\em  multispecies stirring process with open boundaries}. See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.  The bulk part of the model with $N$ species is associated with the integrable ${gl}(N)$ 
Heisenberg XXX Hamiltonian with integrable non-diagonal open boundaries.

@@

The remainder of this paper is organized as follows. In Section~\ref{sec1} we define the open multispecies stirring
process and provide its Lie algebraic description. In Section~\ref{sectionDuality} we prove duality (Theorem~\ref{thm-duality}) 
and we show that, even in the presence of multispecies, the problem of characterizing the non-equilibrium 
steady state can be reduced to the computation of the absorption probabilities. Duality is proved when the 
system has a general spatial structure described by a general graph. In Section~\ref{sectionIntegrabiliy} we then obtain a closed formula 
for the stationary correlations (Theorem~\ref{thm-correlations}) for the case of a one-dimensional chain with at most one 
particle per site, which is driven out-of-equilbrium by two reservoirs acting at the left and right boundaries. 
Here the computation of the absorption probabilities relies on the previously formulated Matrix Product Ansatz \cite{vanicat2017exact},
which is in fact also simplified by the use of duality. Finally in Section~\ref{sec5} we discuss a few extensions 
and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions.

>>>>

{\color{red} Missing the part about non integrable model and duality.}

For the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}. The results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable quantum spin chain, i.e. the XXX Heisenberg Hamiltonian with ${su}(2)$ spins of value $s=1/2$.
In this paper, we investigate the multispecies analog of the exclusion process in the boundary-driven context \cite{vanicat2017exact}, i.e. the {\em  multispecies stirring process with open boundaries}. See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.  The bulk part of the model with $N$ species is associated with the integrable ${gl}(N)$ 
Heisenberg XXX Hamiltonian with integrable non-diagonal open boundaries.

@@

The remainder of this paper is organized as follows. In Section~\ref{sec1} we define the open multispecies stirring
process and provide its Lie algebraic description. In Section~\ref{sectionDuality} we prove duality (Theorem~\ref{thm-duality}) 
and we show that, even in the presence of multispecies, the problem of characterizing the non-equilibrium 
steady state can be reduced to the computation of the absorption probabilities. Duality is proved when the 
system has a general spatial structure described by a general graph. In Section~\ref{sectionIntegrabiliy} we then obtain a closed formula 
for the stationary correlations (Theorem~\ref{thm-correlations}) for the case of a one-dimensional chain with at most one 
particle per site, which is driven out-of-equilbrium by two reservoirs acting at the left and right boundaries. 
Here the computation of the absorption probabilities relies on the extension of the  Matrix Product Ansatz \cite{derrida1993exact} to multiple species \cite{vanicat2017exact},{\color{red}
which is in fact also simplified by the use of duality. }Finally in Section~\ref{sec5} we discuss a few extensions 
and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions.
